Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-10 manuscript/sections/results.tex
results: refine highlights for clarity

\vspace{10pt}
\begin{res}
    24/7 carbon-free electricity (CFE) procurement can eliminate carbon emissiosns of a buyer's electricity consumption and helps to decarbonise the whole electricity system.
\end{res}

\vspace{5pt}
\begin{res}
    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching. 100\% 24/7 CFE can be achieved with solar, wind and battery storage, but at a high cost premium.
\end{res}

The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of \gls{ci} consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
This assumption yields 220~MW of \textbf{base load} that has to be matched with clean electricity. 
The participating consumers can achieve the \gls{cfe} procurement goal by co-optimizing local procurement with of mature technologies (designated as \textbf{palette~1}), i.e., technologies available on a market for commercial use as of now, such as onshore wind, utility-scale solar PV, and battery storage, as well as by importing electricity from the local grid.

%some parts of this paragraph may go to methods
\cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that \gls{ci} consumers follow.
We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (100\% RES) and another case where the consumers commit to 24/7 hourly matching policy with various \gls{cfe} scores in a range from 80\% to 100\%. 
A \textit{reference case} depicts a case when the consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.

@@

\vspace{10pt}
\begin{res}
    24/7 CFE procurement triggers investment in new technologies the system will need later: long-duration storage and advanced clean firm generators.
\end{res}

\vspace*{5pt}
\begin{res}
    High targets for 24/7 CFE procurement could have a much smaller cost premium if long duration energy storage or advanced clean firm technologies are available for a commercial scale up.
\end{res}

@@

\vspace{10pt}
\begin{res}
    Each region of the European electricity system has unique characteristics, such as renewable resources, national policies, degree of interconnection, etc.
    Despite these differences, the model results for 24/7 clean energy procurement show similar trends. 
\end{res}

@@

\vspace{10pt}
\begin{res}
    In 2030, participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
\end{res}

\vspace{5pt}
\begin{res}
    Voluntary commitments to clean electricity procurement bring system value even in
    cleaner grids. Similarly to the base scenario, 24/7 hourly matching results in deeper decarbonisation than 100\% annual renewable matching if CFE targets are above certain treshhold.
\end{res}

@@

\subsection{Exploring mechanisms: how 24/7 CFE procurement decarbonises local grids}
\label{subsec:mechanisms}

\vspace{10pt}
\begin{res}
    24/7 CFE procurement reduces system-level \co \newline
    emissions through "profile" and "volume" mechanisms. 
\end{res}

\vspace{5pt}
\begin{res}
    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies with a cleaner state of local grids. %TODO REFINE
\end{res}

@@

Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE score; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
As for the latter, "excess CFE" might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.

@@

It can be seen in \cref{fig:10-profile-volume.pdf} that the overall impact of 24/7 CFE procurement is proportional to how clean the background grid on average is.
Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB 10\% of \gls{ci} sector participation rate with CFE 100\% score).
It is noteworthy that from 2025 to 2030, the decarbonisation effect of voluntary clean electricity procurement decreases over time in all zones since electricity grids become cleaner as a result of national climate policy programs and decomissioning of emitting power plants.
A comparison of the volume and profile mechanisms reveals that both contribute to the decarbonization of the local grids.
In particular, the profile mechanism contributes significantly to overall emissions reductions, with a major share across all zones regardless of their configuration.

>>>>

\begin{res}
    Through 24/7 CFE procurement, participating consumers can eliminate carbon emissions associated with their electricity consumption and help to decarbonise the entire electricity system.
\end{res}

\begin{res}
    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching. 100\%~CFE target can be achieved with solar PV, wind and battery storage, but at a high cost premium for participating consumers.
\end{res}

%move this up
The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of \gls{ci} consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
This assumption yields 220~MW of \textbf{base load} that has to be matched with clean electricity. 
The participating consumers can achieve the \gls{cfe} procurement goal by co-optimizing local procurement with of mature technologies (designated as \textbf{palette~1}), i.e., technologies available on a market for commercial use as of now, such as onshore wind, utility-scale solar PV, and battery storage, as well as by importing electricity from the local grid.

%some parts of this paragraph may go to methods
\cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that \gls{ci} consumers follow.
We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (100\% RES) and another case where the consumers commit to 24/7 hourly matching policy with various \gls{cfe} targets in a range from 80\% to 100\%. 
A \textit{reference case} depicts a case when the consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.

@@

\begin{res}
    24/7 CFE procurement creates an early market for advanced energy technologies the system will need later: long-duration energy storage and clean firm generators.
\end{res}

\begin{res}
    The cost premium of 24/7 procurement with high CFE targets may substantially decrease if advanced energy technologies available for commercial scale-up. 
\end{res}

@@

\begin{res}
    Despite the inherent variability in regional charac\-teristics---ranging from renewable resources and national policies to degrees of interconnection---the model shows a consistent effects of 24/7 clean energy procurement on both participating buyers and overarching system-level impacts across all analyzed regions.
\end{res}

@@

\begin{res}
    Over time, participating consumers reap benefits from the gradual decline in clean technology costs and a progressively cleaner state of the electricity grids, enhancing the affordability of 24/7 CFE procurement.
\end{res}

\begin{res}
    Voluntary commitments to 24/7 CFE procurement retain their significance in enhancing system value, even as grids become cleaner. Analogous to the base scenario, hourly matching commitments facilitate a more profound decarbonisation compared to 100\% annual renewable matching, provided that CFE targets surpass a particular threshold.
\end{res}

@@

\subsection{Unpacking 24/7 CFE procurement's role in grid decarbonisation}
\label{subsec:mechanisms}

\begin{res}
    24/7 CFE procurement mitigates system-level \co \newline 
    emissions through two distinct mechanisms: "profile" and "volume". The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
\end{res}

\begin{res}
    The disparity in decarbonisation outcomes between 24/7 CFE hourly and 100\% annual renewable matching policies becomes increasingly pronounced as local grids transition to cleaner states. This phenomenon underscores the effectiveness of 24/7 CFE procurement in supporting system decarbonisation in the context of evolving national energy and climate policies.
\end{res}

@@

Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
As for the latter, "excess CFE" might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.

@@

It can be seen in \cref{fig:10-profile-volume.pdf} that the overall impact of 24/7 CFE procurement is proportional to how clean the background grid on average is.
Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB 10\% of \gls{ci} sector participation rate with CFE 100\% target).
It is noteworthy that from 2025 to 2030, the decarbonisation effect of voluntary clean electricity procurement decreases over time in all zones since electricity grids become cleaner as a result of national climate policy programs and decomissioning of emitting power plants.
A comparison of the volume and profile mechanisms reveals that both contribute to the decarbonization of the local grids.
In particular, the profile mechanism contributes significantly to overall emissions reductions, with a major share across all zones regardless of their configuration.
